\documentclass[../main.tex]{subfiles}

\begin{document}
\setcounter{section}{0}
\part{Materials and Methods}

\section{Buffers}

\subsection{Growth Media}
Prepare required volume of Luria Broth. Add appropriate antibiotics to following concentration
\begin{center}
\begin{tabular}{c|c}
\textbf{Antibiotic}&\textbf{Concentration} (\si{\micro\gram\per\milli\litre})\\\hline
Ampicillin & 100\\
Chloramphenicol & 39
\end{tabular}
\end{center}

\subsection{Induction Media}
Prepare growth media with appropriate antibiotic. Add appropriate inducers to following concentration

\begin{center}
\begin{tabular}{c|c}
\textbf{Inducer}&\textbf{Concentration}\\\hline
Arabinose&\SI{100}{\micro\gram\per\milli\litre}\\
IPTG&\SI{25}{\micro\Molar}
\end{tabular}
\end{center}

\subsection{5X Isothermal Buffer}

\begin{center}
\begin{tabular}{c|c|c}
&\textbf{Stock Concentration} (\si{\milli\Molar})&\textbf{Volume} (\si{\micro\litre})\\\hline
PEG-8000					&	25\%		&	\SI{0.75}{\gram}\\
Tris-\ce{HCl} pH 7.5		&	500		&	1500\\
\ce{MgCl2}				&	50		&	75\\
DTT						&	50		&	150\\
dATP						&	1		&	30\\
dTTP						&	1		&	30\\
dCTP						&	1		&	30\\
dGTP						&	1		&	30\\
NAD						&	5		&	300\\
Nuclease free water		&			&	...\\\hline
\textbf{Total}			&	5X		&	3000
\end{tabular}
\end{center}

Use nuclease free water as necessary to make up to \SI{3}{\milli\litre}.

\subsection{Gibson Master Mix}

Prepare on ice in the ligase tube.

\begin{center}
\begin{tabular}{c|c|c}
&\textbf{Stock Concentration} (\si{\unit\per\micro\litre})&\textbf{Volume} (\si{\micro\litre})\\\hline
Taq ligase				&	40		&	50\\
5X Isothermal Buffer		&	5X		&	100\\
T5 Exonuclease			&	1		&	2\\
Phusion Polymerase		&	2		&	6.25\\
Nuclease free water		&			&	216.75\\\hline
\textbf{Total}			&	1.33X	&	375
\end{tabular}
\end{center}

For best performance, aliquot \SIrange{25}{75}{\micro\litre} portions in \SI{1.5}{\milli\litre} microcentrifuge tubes and store at \SI{-20}{\degree}.

\section{Cell Protocols}

\subsection{Overnight Cultures}

Prepare in a 14ml shaky top tube \SI{2}{\milli\litre} growth media with appropriate antibiotic.
Inoculate a single colony in the growth media and grow overnight at \SI{37}{\degree}.

\subsection{Inducing Cultures}

Prepare \SI{2}{\micro\litre} overnight culture. Prepare in a \SI{14}{\micro\litre} shaky top tube \SI{2}{\milli\litre} induction media with appropriate inducer. Inoculate induction media with \SI{20}{\micro\litre} overnight culture.

\subsection{Preparation of \ce{CaCl} Competent Cells}
Prepare \SI{2}{\milli\litre} overnight culture. 
Meanwhile, prewarm \SI{500}{\milli\litre} LB and two \SI{1}{\litre} or one \SI{2}{\litre} conical flasks and pre-cool a centrifuge to \SI{4}{\degree}.
Also cool 16 \SI{1.5}{\milli\litre} microcentrifuge tubes.
Add the overnight culture to the warmed \SI{500}{\milli\litre} in the conical flask(s) and incubate in a shaking incubator for \SIrange{2}{3}{\hour}.
Incubate cells on ice for \si{10}{\minute}.
Spin down cells for \SI{3}{\minute} at 6krpm. Resuspend cells in \SI{10}{\milli\litre} \SI{0.1}{\milli\Molar} \ce{CaCl}.
Incubate cells on ice for \SI{10}{\minute}.
Spin down cells for \SI{3}{\minute} at 6krpm.
Resuspend cells in \SI{5}{\milli\litre} \SI{0.1}{\milli\Molar} \ce{CaCl} in 15\% glycerol.
Alliquot \SI{300}{\micro\litre} into each of the cooled microcentrifuge tubes.
Freeze at \SI{-80}{\degree}.

\subsection{Transformation of \ce{CaCl} Competent Cells}
Thaw \SIrange{20}{200}{\micro\litre} competent cells on ice in \SI{1.5}{\milli\litre} microcentrifuge tubes.
Add \SI{1}{\micro\litre} plasmid DNA or \SI{20}{\micro\litre} ligation assembly DNA or complete Gibson Assembly DNA.
Incubate on ice for \SI{30}{\minute}.
Heat shock for \SIrange{45}{120}{\second} at \SI{42}{\degree}
Incubate on ice for at least \SI{2}{\minute}.
Add \SI{800}{\micro\litre} LB.
Incubate for \SI{1}{\hour} at \SI{37}{\degree} in a shaking incubator.
If required, spin down cells and remove excess LB to concentrate.
Plate out \SIrange{10}{100}{\micro\litre} on LB agar plates with appropriate antibiotic.
Incubate plates overnight at \SI{37}{\degree}.

\subsection{Miniprep}


\subsection{Glycerol Stock}

Prepare \SI{2}{\milli\litre} overnight culture with appropriate antibiotic. Add \SI{250}{\micro\litre} to a \SI{1.5}{\milli\litre} cryogenic tube. Add \SI{1.15}{\micro\litre} overnight culture and mix well. Freeze in \SI{-80}{\degree} freezer.

Source http://web.wi.mit.edu/sive/pub/Lab%20Resources%20Documents/Lab%20Protocols/Maintaining%20plasmid%20stocks.pdf

\subsection{Microscopy Preparation}

\subsubsection{Conventional Microscopy}
Prepare \SI{2}{\milli\litre} overnight culture with appropriate antibiotic.
Pellet the cells in a \SI{1.5}{\milli\litre} microcentrifuge tube.
\paragraph{If fixing}
Resuspend in \SI{500}{\micro\litre} PBS, with or without cobalt.
Add \SI{12.5}{\micro\litre} 37-41\% formaldehyde to make 1\%.
Incubate for 10 minutes at room temperature.
\paragraph{If only adding cobalt}
Resuspend in \SI{500}{\micro\litre} cobalt in PBS.
\paragraph{Then}
Spin down cells.
Resuspend in \SI{1}{\milli\litre} PBS.
Spin down cells.
Resuspend in \SI{500}{\micro\litre} PBS.

\subsubsection{STED Microscopy}
STED microscopy requires a special mounting media to reduce photobleachng.

Prepare cells as above, pelleted. Prepare a a mixture of 1X PBS 90\% glycerol. Prepare a solution of 20\% w/v n-propyl galate in dimethyl sulfoxide. Add 1/100 volume of the 20\% NPG solution to the 1X PBS 90\% glycerol dropwise with rapid stirring. Resuspend the cells in \SI{500}{\micro\litre} of this solution.


\section{DNA Protocols}
\subsection{Restriction Digest}
Prepare on ice in order the following mixture.


\begin{center}
\begin{tabular}{c|c}
				&	\textbf{Volume(\si{\micro\litre})} 	\\\hline
DNA				&	50									\\
Buffer			&	6									\\
Milli Q Water	&	1.4									\\
Enzyme A			&	1									\\
Enzyme B			&	1									\\\hline
\textbf{Total}	&	\textbf{60}					
\end{tabular}
\end{center}

Incubate the mixture at \SI{37}{\degree} in a shaking incubator for 2-3 hours.
If necessary, dephosphorylate the digested product.

\subsection{Dephosphorylation}
Prepare on ice in order the following mixture.

\begin{center}
\begin{tabular}{c|c}
				&	\textbf{Volume(\si{\micro\litre})} 	\\\hline
DNA				&	15									\\
SAP Buffer		&	2									\\
Milli Q Water	&	2									\\
SAP				&	1									\\\hline
\textbf{Total}	&	\textbf{60}					
\end{tabular}
\end{center}

Incubate the mixture at \SI{37}{\degree} for 1-2 hours.

\subsection{PCR}

Prepare in \SI{200}{\micro\litre} PCR tubes in chilled racks the following, in order.

\begin{center}
\begin{tabular}{c|c|c}
&\textbf{Stock Concentration}&\textbf{Volume} (\si{\micro\litre})\\\hline
Reaction Buffer 		&	10X						&	10\\
dNTP					&	\SI{10}{\milli\Molar}	&	5\\
Primer A				&	\SI{100}{\micro\Molar}	&	2.5\\
Primer B				&	\SI{100}{\micro\Molar}	&	2.5\\
Template				&							&	\SI{50}{\nano\gram}\\
\ce{MgCl2}			&	\SI{50}{\micro\Molar}	&	3\\
Polymerase			&							&	1\\
MilliQ water			&							& 	to 50\\\hline
\textbf{Total}		&							&	\textbf{50}
\end{tabular}
\end{center}

Place in a PCR machine and run on the following program.

\begin{center}
\begin{tabular}{c|cc}
\textbf{Step}&\textbf{Temperature}&\textbf{Time}\\\hline
Initial Denaturation	& \SI{98}{\degree} & \SI{120}{\second}\\\hline
\textbf{Loop}&\multicolumn{2}{c}{\textbf{30 times}}\\
Denaturation		&	\SI{98}{\degree}		&	\SI{30}{\second}\\
Annealing 		&	Optimal for primer	&	\SI{30}{\second}\\
Extension		&	\SI{72}{\degree}		&	\SI{30}{\second\per\kilo\base}\\
\textbf{End Loop}	&	& \\\hline
Final extension	&	\SI{72}{\degree}		&	\SI{7}{\minute}\\
Hold				&	\SI{4}{\degree}		&	\(\infty\)
\end{tabular}
\end{center}

\subsection{Diagnostic Gel}

Prepare a small gel of 1\% agarose. Run for one hour etc.

\subsection{Gel Extraction}

\subsection{Gibson Assembly}

Perform PCR as appropriate to obtain overlapping DNA.
Gel extract required bands.
In a PCR tube on ice, add in a 1:1 ratio the overlapping DNA to the 1.33X Gibson Master Mix in a ratio of 1:3 DNA:GMM to a total volume of \SIrange{6}{20}{\micro\litre}.
Incubate the reaction for \SI{1}{\hour} at \SI{50}{\degree}. Incubate on ice or freeze until ready to transform/run on gel.


\subsection{DNA Precipitation}

Prepare on ice the following in a \SI{1.5}{\milli\litre} microcentrifuge tube.
\begin{itemize}
\item At least \SI{50}{\micro\litre} DNA; make up with water as required. This counts as one volume.
\item 1/10 volume \SI{3}{\milli\Molar} \ce{NaOAc}.
\item 2-2.5 volume 100\% \ce{EtOH}.
\end{itemize}
Incubate overnight at \SI{-20}{\degree} or for \SI{1}{\hour} at \SI{-80}{\degree}. Spin down at maximum speed for \SI{30}{\minute} in cooled centrifuge. Suck off supernatent. Resuspend in \SI{100}{\micro\litre} 100\% \ce{EtOH}. Spin down as before in cooled centrifuge. Suck off supernatent. Air dry in flow hood until completely dry. Resuspend in water/TE to volume as appropriate.


\end{document}
